BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-12-04 tex/3-algorithms.tex
up

Properties \ref{wordorderProp} and \ref{lengthProp} are essential to deal with cases where the blog's web feed only contains an abstract or a subset of the entire post article. Table \ref{similarityTable} gives examples to illustrate how these two properties are fulfilled by the Sørensen–Dice coefficient similarity but do not hold for \emph{edit distance} based similarities such as the Levenshtein \cite{levenshtein1966} similarity.

@@

% into: algo 1 defined
With \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as the \code{ScoreFunction}) functions defined, the definition of algorithm \ref{extractionAlgo} for article extraction is completed. We now proceed with a time complexity analysis which will show that this aproach has a quadratic running time.

% algo 1 is quadratic
First, let's assume that we have at our disposal a linear time HTML parser that constructs an appropriate data structure indexing HTML nodes on their \code{id} and \code{class} attributes, effectively making \code{Apply}~$\in$~\Oof{1}. As stated before the outer loop splits the input into independent computations and each call to \coderef{allrulesAlgo} returns (in linear time) at most as many rules as the number of nodes in its \emph{page} argument. Therefore, the body of the inner loop will be executed \Oof{n} times. Because the extraction rule can return any subtree of the queried page, each call to \coderef{similarityAlgo} takes \Oof{n}, leading to an overall quadratic running time.

% linear reformulation
We now present Algorithm \ref{linearAlgo}, linear time reformulation of Algorithm \ref{extractionAlgo} for article extraction using dynamic programming. While very intuitive, the original idea of first generating extraction rules and then picking these best rules prevents us from an effective reuse of previously computed bigrams. For instance, when evaluating the extraction rule for the HTML root node, Algorithm \ref{extractionAlgo} will obtain the complete string of the page and pass it to the \coderef{similarityAlgo} function. At this point, the information on where the string could be split into substrings with already computed bigrams is not accessible, and the bigrams of the page have to be computed by linearly traversing the entire string. To overcome this limitation and implement \emph{memoization} over the bigrams computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree to compute node bigrams from their children bigrams. This way we avoid serializing HTML subtrees for each bigrams computation and have the guarantee that each character of the HTML page will be read at most once during the bigrams computation.

@@

% proof
With bigrams computed in a dynamic programming manner, the cumulated time needed to compute \coderef{bigramsAlgo}\code{(}\emph{node.text}\code{)} is linear. To conclude the proof that algorithm \ref{linearAlgo} runs in linear time we show that all other computations of the inner loop can be done in constant \emph{amortized} time. As the number of edges in a tree is one less than the number of nodes, the \emph{amortised} number of bigrams unions per inner loop iteration tends to one. Each \emph{quotient of similarity} computation requires one bigrams intersection and three bigrams length computations. Over a finite alphabet (we used printable ASCII), bigrams sizes have bounded size and each of these operations takes constant time.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Variations for authors, dates, comments}
\label{variationsforauthorsdatesandcomments}

% intro
Using string similarity as only score measurement leads to poor performances on authors and dates extraction and is not suitable for comment extraction. This subsection presents variations of the previously presented \code{ScoreFunction} which address issues of these other contents.

% authors
The case of authors is problematic because it is not uncommon to encounter the author's name at several places in a page, which results in several rules with maximum \coderef{similarityAlgo} score. The heuristic we use to get around this issue consists of adding a new component in the \code{ScoreFunction} for authors extraction rules: the \emph{tree distance} between the evaluated node and the post content node. This new component takes advantage of the positioning of post's authors which often is a direct child or shares its parent with the post content node.

% dates
Dates are affected by the same duplication issue, as well as the inconsistence of format between web feeds and web pages. Our solution for dates extraction extends authors \code{ScoreFunction} by comparing the \emph{extracted} string to multiple \emph{targets}, each being a different string representation of the original \emph{target} date obtained from the web feed. For instance, if the feed indicates that a post was published on \stringliteral{Thu, 01 Jan 1970 00:00:00}, our algorithm will search for a rule that returns one of \stringliteral{Thursday January 1, 1970}, \stringliteral{1970-01-01}, \stringliteral{43 years ago} and so on. We use a total of 8 target date formats that was empirically built during our experiments. While this list is certainly not exhaustive, our approach using string similarity on multiple target dates is tolerant to small variations. So far we do not support dates in multiple languages, but adding new target formats base and languages detection would be a simple extension of our date extraction algorithm.

% comments
Comments are usually available in separate web feeds, one per blog post. Similarly to blog feeds, comment feeds have a limited number of entries, and in case a blog post has more comments than the ones appearing in the feed, comments have to be extracted from the post web page. To do so we use the following \code{ScoreFunction}:
\begin{itemize}
  \item Rules returning less HTML nodes than the number of comments on the feed are filtered out with a zero score.
  \item Remaining rules are scored with the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ as weight equal to \code{\ref{similarityAlgo}(}$u, v$\code{)}.
\end{itemize}
Our crawler executes this algorithm on each post with overflow on its comment feed, thus supporting blogs with multiple commenting engines. Comment contents are extracted first, which allows to narrow down the initial filtering by fixing a target number of comments.

% rush some time complexity analysis
Regarding time complexity, computing the \emph{tree distance} of all nodes of a graph to a single reference node can be done in linear time, and multiplying the number of targets by a constant factor does not affects the asymptotic computational complexity. While evaluating rules for comments extraction requires more a expensive algorithm, the proportion of candidates left after filter out comment rules with an insufficient number of results was very low in practice. Analog  reformulations to the one explained in \ref{timecomplexityandlinearreformulation} can be applied for each \code{ScoreFunction} in order to minimize the time spent in \coderef{similarityAlgo}.

>>>>

Properties \ref{wordorderProp} and \ref{lengthProp} are essential to deal with cases where the blog's web feed only contains an abstract or a subset of the entire post article. Table \ref{similarityTable} gives examples to illustrate how these two properties hold for the Sørensen–Dice coefficient similarity but do not for \emph{edit distance} based similarities such as the Levenshtein \cite{levenshtein1966} similarity.

@@

% into: algo 1 defined
With functions \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as the \code{ScoreFunction}) defined, the definition of Algorithm \ref{extractionAlgo} for article extraction is completed. We now proceed with a time complexity analysis.

% algo 1 is quadratic
First, let's assume that we have at our disposal a linear time HTML parser that constructs an appropriate data structure indexing HTML nodes on their \code{id} and \code{class} attributes, effectively making \code{Apply}~$\in$~\Oof{1}. As stated before the outer loop splits the input into independent computations and each call to \coderef{allrulesAlgo} returns (in linear time) at most as many rules as the number of nodes in its \emph{page} argument. Therefore, the body of the inner loop will be executed \Oof{n} times. Because each extraction rule can return any subtree of the queried page, each call to \coderef{similarityAlgo} takes \Oof{n}, leading to an overall quadratic running time.

% linear reformulation
We now present Algorithm \ref{linearAlgo}, a linear time reformulation of Algorithm \ref{extractionAlgo} for article extraction using dynamic programming. While very intuitive, the original idea of first generating extraction rules and then picking these best rules prevents us from effectively reusing previously computed bigrams. For instance, when evaluating the extraction rule for the HTML root node, Algorithm \ref{extractionAlgo} will obtain the complete string of the page and pass it to the \coderef{similarityAlgo} function. At this point, the information on where the string could be split into substrings with already computed bigrams is not accessible, and the bigrams of the page have to be computed by linearly traversing the entire string. To overcome this limitation and implement \emph{memoization} over the bigrams computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree and computes node bigrams from their children bigrams. This way, we avoid serializing HTML subtrees for each bigrams computation and have the guarantee that each character of the HTML page will be read at most once during the bigrams computation.

@@

% proof
With bigrams computed in this dynamic programming manner, the total time needed to compute all \coderef{bigramsAlgo}\code{(}\emph{node.text}\code{)} is linear. To conclude the proof that Algorithm \ref{linearAlgo} runs in linear time we show that all other computations of the inner loop can be done in constant \emph{amortized} time. As the number of edges in a tree is one less than the number of nodes, the \emph{amortised} number of bigrams unions per inner loop iteration tends to one. Each \emph{quotient of similarity} computation requires one bigrams intersection and three bigrams length computations. Over a finite alphabet (we used printable ASCII), bigrams sizes have bounded size and each of these operations takes constant time.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Variations for authors, dates, comments}
\label{variationsforauthorsdatesandcomments}

% intro
Using string similarity as only score measurement leads to poor performances on authors and dates extraction, and is not suitable for comment extraction. This subsection presents variations of the previously presented \code{ScoreFunction} which address issues of these other contents.

% authors
The case of authors is problematic because authors' names often appears in multiple places of a page, which results in several rules with maximum \coderef{similarityAlgo} score. The heuristic we use to get around this issue consists of adding a new component in the \code{ScoreFunction} for authors extraction rules: the \emph{tree distance} between the evaluated node and the post content node. This new component takes advantage of the positioning of post's authors which often is a direct child or shares its parent with the post content node.

% dates
Dates are affected by the same duplication issue, as well as the inconsistence of format between web feeds and web pages. Our solution for dates extraction extends the \code{ScoreFunction} for authors by comparing the \emph{extracted} string to multiple \emph{targets}, each being a different string representation of the original date obtained from the web feed. For instance, if the feed indicates that a post was published on \stringliteral{Thu, 01 Jan 1970 00:00:00}, our algorithm will search for a rule that returns one of \stringliteral{Thursday January 1, 1970}, \stringliteral{1970-01-01}, \stringliteral{43 years ago} and so on. So far we do not support dates in multiple languages, but adding new target formats base and languages detection would be a simple extension of our date extraction algorithm.

% comments
Comments are usually available in separate web feeds, one per blog post. Similarly to blog feeds, comment feeds have a limited number of entries, and when the number of comments on a blog post exceeds this limit, comments have to be extracted from the post web page. To do so we use the following \code{ScoreFunction}:
\begin{itemize}
  \item Rules returning less HTML nodes than the number of comments on the feed are filtered out with a zero score,
  \item Remaining rules are scored with the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ as weight equal to \code{\ref{similarityAlgo}(}$u, v$\code{)}.
\end{itemize}
Our crawler executes this algorithm on each post with overflow on its comment feed, thus supporting blogs with multiple commenting engines. Comment contents are extracted first, which allows to narrow down the initial filtering by fixing a target number of comments.

% rush some time complexity analysis
Regarding time complexity, computing the \emph{tree distance} of each nodes of a graph to a single reference node can be done in linear time, and multiplying the number of targets by a constant factor does not affects the asymptotic computational complexity. While scoring rules for comments extraction requires a more expensive algorithm, the proportion of candidates left after filter out rules with an insufficient number of results is very low in practice. Analog reformulations to the one done with Algorithm \ref{linearAlgo} can be applied on each \code{ScoreFunction} in order to minimize the time spent in \coderef{similarityAlgo}.

### 2013-12-04 tex/4-techniques.tex
Small changes after skype call + end of algorithms section.
up

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{JavaScript rendering}
% Introduction
JavaScript is a widely used language for client-side web scripting. While some applications simply use it for aesthetics (menus, animations...), an increasing number of websites use JavaScript to download and display content. In such cases, traditional HTML based crawled do not see web pages as they would be presented to a human visitor and might therefore be obsolete for data extraction.

% Motivation
In our experiments crawling the blog sphere, we encountered several blogs where data was missed because of the lack of JavaScript interpretation. The most frequent cases where blogs using the Disqus \cite{disqus2013} and LiveFyre \cite{livefyre2013} comment hosting services. These tools are very handy to setup for web-masters because the entire comments infrastructure is externalized and the setup essential comes down to including a JavaScript snippet in each target page. Both of these services heavily rely on JavaScript to download and display the comments, even providing functionalities such as real-time updates for edits and newly written comments. Less commonly, some blogs are fully rendered using JavaScript. When loading such website, the web browser will not receive the page content as an HTML file, but will instead have execute JavaScript code to download and display the page content. One example can be found on the Blogger platforms which provides as one of its default templates the \emph{Dynamic Views} which use this mechanism \cite{antinharasymiv2011}.

% The solution
To support blogs with JavaScript generated content, we embed a full web browser into the crawler. After considering multiple option, we opted for PhantomJS \cite{phantomjs2013}, a headless web browser with great performances and scripting capabilities. The JavaScript rendering is done as the very first step of web page processing. Extracting blog post content, comments or medias therefore works equally well on both blogs with JavaScript generated content and traditional HTML-only blogs.

% Click click scripting
When the number of comments on one page exceeds a certain threshold, both Disqus and LiveFyre only load a subset of them and end the stream of comments with a \emph{Show More Comments} buttons. As part of the page loading process, we instruct PhantomJS to repeatedly click on these buttons until all comments are loaded. Paths to Disqus and LiveFyre \emph{show more} buttons were manually obtained and are the only non-generic element of the extraction stack which will require human intervention to maintain and extend to other commenting platforms.

@@

Our use case has two types of spiders: \emph{NewCrawl} and \emph{UpdateCrawl}, which respectively implement the logic to crawl a new blog and to get updates from a previously crawled blog. After beeing downloaded and identified as blog posts (details in subsection \ref{enrichingscrapy}), pages are packed into \emph{Items} and sent through the following pipeline of operation:
\begin{enumerate}[noitemsep]
  \item Render JavaScript
  \item Extract content
  \item Extract comments
  \item Download medias
  \item Propagate resulting records to the Invenio back-end
\end{enumerate}
This pipeline design, often called \emph{pipes and filters pattern} \cite[Chapter Messaging Systems]{hohpe2003}, provides great modularity. Indeed, disabling JavaScript rendering or plugging in an alternative back-end can be done by editing a single line of code.

@@

% blog post identification
Given an entry point to a website, the default Scrapy behavior allows to look over all pages of the same domain in a \emph{last-in-first-out} manner. The \emph{blog post identification} function is able to identify from an URL whether or not the corresponding page is a blog post. Internally, this function uses a per blog regular expression constructed from web feed entry URLs. This simple approach requires that blogs use the same pattern for all posts (or false negative will occur) which has to be distinct for non-post pages (or false positive will occur). In practice this assumption held for all blog platforms we encountered during the developments and seems to be a common practice among web developer.

% download priority heuristic
In order to efficiently deal with blogs with a large number of non-blog-post pages, this blog post identification mechanism is not sufficient. Indeed, after all pages identified as blog post are processed, the crawler needs to download non-blog post pages to search for additional blog posts. To replace the naive random walk, depth first search or breadth first search web site traversals, we use a priority queue where new URL priorities are determined using a simple machine learning algorithm. Given an URL, the machine learning system does an estimation on the number of links to blog post the corresponding page will contain. This estimated number of links are then used as a \emph{download priorities} to decide the best URL to visit next. Each time a page is effectively downloaded, the actual number of blog post links it contains is computed and passed to the machine learning system as training data that will then be taken into account during future predictions. This mechanism has shown to be indispensable for blogs hosting on the single domain a large number of non-blog web pages, such as a forum or a wiki.

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scalability}
When aiming to work with a large number of inputs, it is crucial to build every layer of the system with scalability in mind\cite{thereactivemanifesto2013}. At the time of writing we did not had the chance to work on the deployment of the BlogForever project on a distributed environment. However, the BlogForever crawler, and in particular the two core procedures \emph{NewCrawl} and \emph{UpdateCrawl}, are designed to be usable as part of an event-driven, scalable and fault resilient distributed system.

To achieve this property we made the key design choice to have both \emph{NewCrawl} and \emph{UpdateCrawl} as stateless components. Indeed, from a high level viewpoint, these two components are \emph{purely functional}:
%
\newcommand\URL{\mathbb{U}\text{RL}}
\newcommand\DATE{\mathbb{D}\text{ATE}}
\newcommand\RECORD{\mathbb{R}\text{ECORD}}
\begin{equation*}
  \begin{split}
    NewCrawl:    &~ \URL \rightarrow \mathcal{P}(\RECORD)\\
    UpdateCrawl: &~ \URL \times \DATE \rightarrow \mathcal{P}(\RECORD)
  \end{split}
\end{equation*}
Where $\URL$, $\DATE$ and $\RECORD$ are respectively the set of all URLs, dates and records, and $\mathcal{P}(\cdot)$ designates the powerset. By delegating all shared mutable state to the backend system (Invenio's database), web crawler instances can be added, removed, and used interchangeably.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{JavaScript rendering}
% Introduction
JavaScript is a widely used language for client-side web scripting. While some applications simply use it for aesthetics (menus, animations...), an increasing number of websites use JavaScript to download and display content. In such cases, traditional HTML based crawled do not see web pages as they are presented to a human visitor and might therefore be obsolete for data extraction.

% Motivation
In our experiments crawling the blog sphere, we encountered several blogs where data was missed because of the lack of JavaScript interpretation. The most frequent cases where blogs using the Disqus \cite{disqus2013} and LiveFyre \cite{livefyre2013} comment hosting services. These tools are very handy to setup for web-masters because the entire comments infrastructure is externalized and the setup essential comes down to including a JavaScript snippet in each target page. Both of these services heavily rely on JavaScript to download and display the comments, even providing functionalities such as real-time updates for edits and newly written comments. Less commonly, some blogs are fully rendered using JavaScript. When loading such website, the web browser will not receive the page content as an HTML file, but will instead have to execute JavaScript code to download and display the page content. The Blogger platforms provides as a default templates the \emph{Dynamic Views}, which use this mechanism \cite{antinharasymiv2011}.

% The solution
To support blogs with JavaScript generated content, we embed a full web browser into the crawler. After considering multiple option, we opted for PhantomJS \cite{phantomjs2013}, a headless web browser with great performances and scripting capabilities. The JavaScript rendering is done as the very first step of web page processing. Extracting blog post articles, comments or medias therefore works equally well on blogs with JavaScript generated content and traditional HTML-only blogs.

% Click click scripting
When the number of comments on a page exceeds a certain threshold, both Disqus and LiveFyre will only load the most recent ones and the stream of comments will end with a \emph{Show More Comments} buttons. As part of the page loading process, we instruct PhantomJS to repeatedly click on these buttons until all comments are loaded. Paths to Disqus and LiveFyre \emph{show more} buttons were manually obtained and are the only non-generic element of our extraction stack which will require human intervention to maintain and extend to other commenting platforms.

@@

Our use case has two types of spiders: \emph{NewCrawl} and \emph{UpdateCrawl}, which respectively implement the logic to crawl a new blog and to get updates from a previously crawled blog. After beeing downloaded and identified as blog posts (details in \ref{enrichingscrapy}), pages are packed into \emph{Items} and sent through the following pipeline of operation:
\begin{enumerate}[noitemsep]
  \item Render JavaScript
  \item Extract content
  \item Extract comments
  \item Download medias
  \item Propagate resulting records to the back end
\end{enumerate}
This pipeline design provides great modularity. Indeed, disabling JavaScript rendering or plugging in an alternative back-end can be done by editing a single line of code.

@@

% blog post identification
Given an entry point to a website, the default Scrapy behavior looks over all pages of the same domain in a \emph{last-in-first-out} manner. The \emph{blog post identification} function is able to identify from an URL whether or not the corresponding page is a blog post. Internally, this function uses a per blog regular expression constructed from web feed entry URLs. This simple approach requires that blogs use the same pattern for all posts (or false negative will occur) which has to be distinct for non-post pages (or false positive will occur). In practice this assumption held for all blog platforms we encountered and seems to be a common practice among web developer.

% download priority heuristic
In order to efficiently deal with blogs with a large number of non-blog-post pages, this \emph{blog post identification} mechanism is not sufficient. Indeed, after all pages identified as blog post are processed, the crawler needs to download non-blog-post pages to search for additional blog posts. To replace the naive random walk, depth first search or breadth first search web site traversals, we use a priority queue where new URL priorities are determined by a simple machine learning algorithm. Given an URL, the machine learning system does an estimation on the number of links to blog post the corresponding page will contain. This estimated number of links are then used as \emph{download priorities} to decide the best URL to visit next. Each time a page is effectively downloaded, the actual number of blog post links it contains is computed and passed to the machine learning system as training data will then be taken into account during future predictions. This mechanism has shown to be indispensable for blogs hosting on the single domain a large number of non-blog web pages, such as a forum or a wiki.

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scalability}
When aiming to work with a large number of inputs, it is crucial to build every layer of the system with scalability in mind\cite{thereactivemanifesto2013}. The BlogForever crawler, and in particular the two core procedures \emph{NewCrawl} and \emph{UpdateCrawl}, are designed to be usable as part of an event-driven, scalable and fault resilient distributed system.

To achieve this property we made the key design choice to have both \emph{NewCrawl} and \emph{UpdateCrawl} as stateless components. From a high level viewpoint, these two components are \emph{purely functional}:
%
\newcommand\URL{\mathbb{U}\text{RL}}
\newcommand\DATE{\mathbb{D}\text{ATE}}
\newcommand\RECORD{\mathbb{R}\text{ECORD}}
\begin{equation*}
  \begin{split}
    NewCrawl:    &~ \URL \rightarrow \mathcal{P}(\RECORD)\\
    UpdateCrawl: &~ \URL \times \DATE \rightarrow \mathcal{P}(\RECORD)
  \end{split}
\end{equation*}
Where $\URL$, $\DATE$ and $\RECORD$ are respectively the set of all URLs, dates and records, and $\mathcal{P}(\cdot)$ designates the powerset. By delegating all shared mutable state to the back end system (Invenio's database), web crawler instances can be added, removed, and used interchangeably.
